Response to the defense feedback

### 2021-06-19 Chapter-5/Chapter-5.tex
Updates from Overleaf

Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \ctool{} and \tool{}~\cite{bao2021abacus}. According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero. As the result indicates, the leakage sites that leak a lot of information (> 5.0 bits) are all fixed in OpenSSL 1.1.1. The result indicates that \ctool{} can help developers identify side-channel leakages and pick severe ones from them automatically. As expected, we find that most of the leakages are from the big number calculations. OpenSSL has a side-channel mitigated big number implementation. As long as big numbers are derived from the secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}. However, the flag is off by default. We find that the developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.

@@

Previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerabilities are severe. Previous work \tool{}~\cite{bao2021abacus} quantifies the amount of leaked information for one execution. So it is possible that some leakage sites leak little information for one input but leak more information for a different input. We run the chi-squared test to determine if any two leaked functions have independent leakages. However, we cannot conclude that any two leakages from cryptography benchmarks are independent under the chi-squared test. We think it is probably due to the avalanche effect in cryptography.

@@

We evaluate \ctool{} on TinyDNN, a deep learning framework in C++. We
construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with
the MINIST dataset. LeNet-5 network has six layers, including three
convolutional layers, one fully connected layer, and two pooling
layers. The batch size in our experiment is 10, and the number of
epochs is 30. After the training, the accuracy of the neural networks
on test set images is 99.5\%. Then we use the model to infer the
images. The inference dataset consists of $10,000$ images.  During the
inference, we record the memory access information. The evaluation
shows all three types of layers have different memory accesses under
different inputs. We find that the leakages primarily come from the
activation function and the image convert function.

>>>>

Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \ctool{} and \tool{}~\cite{bao2021abacus}. According to \tool{}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero. As the result indicates, the leakage sites that leak a lot of information (> 5.0 bits) are all fixed in OpenSSL 1.1.1. The result indicates that \ctool{} can help developers identify side-channel leakages and pick severe ones from them automatically. As expected, we find that most of the leakages are from the big number calculations. OpenSSL has a side-channel mitigated big number implementation. As long as big numbers are derived from the secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}. However, the flag is off by default. We find that the developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}.

@@

Previous work~\cite{bao2021abacus} reports some leakage sites leak little information, but \ctool{} reports the vulnerabilities are severe. \tool{} quantifies the amount of leaked information for one execution. So it is possible that some leakage sites leak little information for one input but leak more information for a different input. We run the chi-squared test to determine if any two leaked functions have independent leakages. However, we cannot conclude that any two leakages from cryptography benchmarks are independent under the chi-squared test. We think it is probably due to the avalanche effect in cryptography.

@@

We evaluate \ctool{} on TinyDNN, a deep learning framework in C++. We
construct a LeNet-5 model~\cite{lecun1998gradient} and train it with
the MINIST dataset. LeNet-5 network has six layers, including three
convolutional layers, one fully connected layer, and two pooling
layers. The batch size in our experiment is 10, and the number of
epochs is 30. After the training, the accuracy of the neural networks
on test set images is 99.5\%. Then we use the model to infer the
images. The inference dataset consists of $10,000$ images.  During the
inference, we record the memory access information. The evaluation
shows all three types of layers have different memory accesses under
different inputs. We find that the leakages primarily come from the
activation function and the image convert function.
